---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English - Part 2"
author: Anonymous
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: html_document
---

# Introduction{-}

This document shows an analysis of adjective amplification in Hong Kong, Indian , and Philippine English based on the respective components of the International Corpus of English (ICE).  

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```


## Preparation{-}

Package installation

```{r install, eval = F, message = F, warning = F}
install.packages("tidyverse")
install.packages("tidyr")
install.packages("here")
install.packages("car")
install.packages("caret")
install.packages("here")
install.packages("randomForest")
install.packages("rms")
install.packages("lme4")
install.packages("lmerTest")
install.packages("utils")
install.packages("sjPlot")
install.packages("effects")
install.packages("simr")
install.packages("lattice")
install.packages("Matrix")
install.packages("DescTools", dependencies = T)
```

* set options

* activate packages

* load functions.

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# load packages
library(tidyverse)
library(tidyr)
library(here)
library(ggparty)
library(partykit)
library(caret)
library(DescTools)
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)   
```

## Load data{-}

```{r amphkpie_02_03, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- base::readRDS(file = here::here("data", "iceamp_prefinal.rda"))
# inspect
head(ice)
```

## Clean data

check date distribution

```{r}
table(ice$Corpus, ice$Date)
```

check age distribution

```{r}
table(ice$Corpus, ice$Age)
```


```{r}
ice %>%
  dplyr::group_by(Adjective) %>%
  dplyr::summarise(Gradability = mean(Gradability)) %>%
  ggplot(aes(Adjective, Gradability, label=Adjective)) +
  geom_text(size = 2)
```


Factorize predictors and scale frequency

```{r amphkpie_02_05, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  select(-Id, -PreContext, -Token, -L1, -Postag, -PostContext, -PreContextLong, -Nationality, -OtherLanguages, -Birthplace) %>%
  dplyr::mutate_if(is.character, factor) %>%
  dplyr::mutate(Speaker = paste0(Corpus, ":", File, "$", Speaker),
                Variety = dplyr::case_when(Corpus == "ICE-HK" ~ "HKE",
                                           Corpus == "ICE-IND" ~ "IndE",
                                           Corpus == "ICE-PHI" ~ "PhiE",
                                           T ~ Corpus)) %>%
  dplyr::mutate(Age = dplyr::case_when(Age == "17-25" ~ "16-25",
                                       Age == "18-25" ~ "16-25",
                                       Age == "26-41" ~ "26-40",
                                       Age == "42+" ~ "41+",
                                       T ~ Age)) %>%
  dplyr::mutate(Date = as.numeric(as.character(Date)),
                Date = ifelse(Date < 1998, "1997-", "1998+")) %>%
  dplyr::mutate_if(is.character, factor)
# inspect
str(ice)
```

```{r}
amp <- ice %>%
  dplyr::filter(Variant != "0")
```

check semantic categories distribution

```{r}
ice %>%
  dplyr::filter(SemanticCategory == "other") %>%
  dplyr::group_by(Adjective) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::sample_n(20) 
```

save data

```{r}
base::saveRDS(ice, file = here::here("data", "ice_final.rda"))
```



# Visualization

```{r message=F, warning=F}
ice %>%
  # data prep
  dplyr::group_by(Variety, Amplified, Function) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::group_by(Variety) %>%
  dplyr::mutate(Total = sum(Freq),
                Percent = round(Freq/Total*100, 1),
                Label = paste0(Percent, " (", Freq, ")")) %>%
  dplyr::filter(Amplified == 1) %>%
  # plot
  ggplot(aes(x=Variety, y= Percent, group = Function, fill = Function, label = Label)) +          
  geom_text(aes(y = Percent + 1), position = position_dodge(0.9), size=3) +     
  geom_bar(stat = "identity", position = position_dodge()) + 
  coord_cartesian(ylim = c(0, 20)) +
  theme_bw(base_size = 10) +         
  theme(axis.text.x = element_text(size=10),  
        axis.text.y = element_text(size=10, face="plain"),
        legend.position = "top") + 
  labs(x = "Variety of English", y = "Percent (of Amplification)") +     
  scale_fill_manual(values = c("gray80", "gray40")) 
# save
ggsave(here::here("images", "Fig2.png"), width = 15, height = 10,unit = "cm")
```


```{r message=F, warning=F}
amp %>%
  dplyr::group_by(Variety, Variant) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::group_by(Variety) %>%
  dplyr::mutate(Total = sum(Freq),
                Percent = round(Freq/Total*100, 1),
                Label = paste0(Percent, " (", Freq, ")")) %>%
  dplyr::group_by(Variant) %>%
  dplyr::mutate(VarFreq = sum(Freq)) %>%
  dplyr::filter(VarFreq > 4) %>%
  # start plot
  ggplot(aes(x=reorder(Variant, VarFreq), y = Percent, label = Label)) + 
  geom_text(hjust = -0.1, size=3, angle = 0) +     
  geom_bar(stat = "identity") + 
  coord_flip(ylim = c(0, 119)) +
  theme_bw(base_size = 10) +         
  theme(axis.text.x = element_text(size=10),  
        axis.text.y = element_text(size=10, face="plain"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  labs(x = "Amplifier Variant (only N 5+)", y = "Percent (N)") +     
  scale_color_manual(guide = FALSE) +
  facet_wrap(~Variety)
# save
ggsave(here::here("images", "Fig1_reduced.png"), width = 15, height = 8, unit = "cm")
```

```{r message=F, warning=F}
amp %>%
  dplyr::group_by(Variety, Variant) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::group_by(Variety) %>%
  dplyr::mutate(Total = sum(Freq),
                Percent = round(Freq/Total*100, 1),
                Label = paste0(Percent, " (", Freq, ")")) %>%
  dplyr::group_by(Variant) %>%
  dplyr::mutate(VarFreq = sum(Freq)) %>%
  #dplyr::filter(VarFreq > 4) %>%
  # start plot
  ggplot(aes(x=reorder(Variant, VarFreq), y = Percent, label = Label)) + 
  geom_text(hjust = -0.1, size=3, angle = 0) +     
  geom_bar(stat = "identity") + 
  coord_flip(ylim = c(0, 119)) +
  theme_bw(base_size = 10) +         
  theme(axis.text.x = element_text(size=10),  
        axis.text.y = element_text(size=10, face="plain"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  labs(x = "Amplifier Variant (only N 5+)", y = "Percent (N)") +     
  scale_color_manual(guide = FALSE) +
  facet_wrap(~Variety)
# save
ggsave(here::here("images", "Fig1.png"), width = 15, height = 15, unit = "cm")
```





## Data Reduction

Determine adjective frequency

```{r amphkpie_02_07, echo=T, eval = T, message=FALSE, warning=FALSE}
fadj <- names(table(amp$Adjective))[which(table(amp$Adjective) > 25)]
fadj
```

Determine variant frequency

```{r amphkpie_02_09, echo=T, eval = T, message=FALSE, warning=FALSE}
famp <- names(table(amp$Variant))[which(table(amp$Variant) > 50)]
famp
```



Collapse infrequent adjectives and amplifiers



```{r amphkpie_02_11,  message=TRUE, warning=TRUE}
amp <- amp %>%
  dplyr::mutate(Frequency = round(Frequency, 3),
                Gradability = round(Gradability, 3),
                Adjective = dplyr::case_when(Adjective %in% fadj ~ Adjective, 
                                             T ~ "other"),
                SVariant = Variant, 
                Variant = dplyr::case_when(Variant %in% famp ~ Variant, 
                                           T ~ "other")) %>%
  dplyr::select(-Corpus, -Amplified, -File) %>%
  dplyr::mutate_if(is.character, factor) %>%
  droplevels()
# inspect
str(amp)
```

save data

```{r}
base::saveRDS(amp, file = here::here("data", "amp_final.rda"))
```

## Visualisation

```{r message=F, warning=F}
amp %>%
  # prep
  dplyr::group_by(Variety, Function, Age, Variant) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::group_by(Variety, Function, Age) %>%
  dplyr::mutate(Total = sum(Freq),
                Percent = round(Freq/Total*100, 1)) %>%
  dplyr::mutate_if(is.character, factor) %>%
  # plot
  ggplot(aes(y = Percent, x = Age, linetype = Variant, shape = Variant, group = Variant)) +
  geom_line(size = .5) +
  geom_point(shape = 19, size=8, colour="white") + 
  geom_point(size = 3) +
  scale_shape_manual(values = c("o", "r", "s", "v")) +
  facet_grid(Function~Variety) +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(size=10),  
        axis.text.y = element_text(size=10, face="plain"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_cartesian(ylim = c(0, 119))
# save
ggsave(here::here("images", "Fig3.png"), width = 15, height = 10,unit = "cm")
```




## Tabulation


```{r}
# process
tb1a <- amp %>%
  dplyr::group_by(Variety, Age, Gender) %>%
  dplyr::summarize(Adjectives = n(),
            VariantType = names(table(Variant)),
            VariantsN = table(Variant),
            VariantsP = round(VariantsN/Adjectives*100, 1),
            Percent = paste0(VariantsP, "% (N=", VariantsN, ")")) %>%
  dplyr::select(-VariantsN, -VariantsP) %>%
  tidyr::spread(VariantType, Percent) %>%
  dplyr::ungroup()
# save
writexl::write_xlsx(tb1a, here::here("tables", "tb1a.xlsx"))
# inspect data
tb1a
```


```{r}
tb1b <- amp %>%
  dplyr::mutate(Variant = dplyr::case_when(Variant == "very" ~ "very",
                                           Variant == "really" ~ "really",
                                           Variant == "so" ~ "so",
                                           T ~ "other")) %>%
  dplyr::group_by(Variety) %>%
  dplyr::reframe(Speakers = length(names(table(Speaker)[table(Speaker) > 0])),
                 Adjectives = n(),
                 VariantType = names(table(Variant)),
                 VariantsN = table(Variant),
                 VariantsP = round(VariantsN/Adjectives*100, 1),
                 Percent = paste0(VariantsP, "% (N=", VariantsN, ")")) %>%
  dplyr::select(-VariantsN, -VariantsP) %>%
  tidyr::spread(VariantType, Percent) %>%
  dplyr::ungroup() %>%
  tibble::add_row(Variety = "Total",
                  Speakers = sum(.$Speakers),
                  Adjectives = sum(.$Adjectives),
                  other = as.character(sum(as.numeric(gsub(".*\\=([0-9]{1,})\\)", "\\1", .$other)))),
                  really = as.character(sum(as.numeric(gsub(".*\\=([0-9]{1,})\\)", "\\1", .$really)))),
                  so = as.character(sum(as.numeric(gsub(".*\\=([0-9]{1,})\\)", "\\1", .$so)))),
                  very = as.character(sum(as.numeric(gsub(".*\\=([0-9]{1,})\\)", "\\1", .$very))))) %>%
  dplyr::mutate(other = ifelse(Variety == "Total", paste0(round(as.numeric(other)/Adjectives*100, 1), "% (N=", other, ")"), other),
                really = ifelse(Variety == "Total", paste0(round(as.numeric(really)/Adjectives*100, 1), "% (N=", really, ")"), really),
                so = ifelse(Variety == "Total", paste0(round(as.numeric(so)/Adjectives*100, 1), "% (N=", so, ")"), so),
                very = ifelse(Variety == "Total", paste0(round(as.numeric(very)/Adjectives*100, 1), "% (N=", very, ")"), very))
# save
writexl::write_xlsx(tb1b, here::here("tables", "tb1b.xlsx")) 
# inspect data
tb1b
```


```{r}
amp %>%
  dplyr::group_by(Variety, Speaker) %>%
  dplyr::summarise(Frequency = n()) %>%
  dplyr::arrange(-Frequency) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Variety) %>%
  dplyr::mutate(Speaker = 1:n()) %>%
  dplyr::ungroup() %>%
  ggplot(aes(x = Speaker, y = Frequency, group = Variety, fill = Variety)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Variety) +
  theme_bw() +
  theme(legend.position = "top") +
  scale_color_manual(values = c("gray80", "gray50", "gray20"))
```

# Preparation for stats 

## Clean data

check amplifiers by variety

```{r}
amp %>%
  dplyr::filter(Variety == "IndE") %>%
  dplyr::group_by(SVariant) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(All = sum(Freq)) %>%
  dplyr::summarise(NVariants = nrow(.),
                   NAdjs = unique(All),
                   Rate = round(NAdjs/NVariants, 1))
```


```{r}
amp %>%
  dplyr::filter(Variety == "HKE") %>%
  dplyr::group_by(SVariant) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(All = sum(Freq)) %>%
  dplyr::summarise(NVariants = nrow(.),
                   NAdjs = unique(All),
                   Rate = round(NAdjs/NVariants, 1))
```

```{r}
amp %>%
  dplyr::filter(Variety == "PhiE") %>%
  dplyr::group_by(SVariant) %>%
  dplyr::summarise(Freq = n()) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(All = sum(Freq)) %>%
  dplyr::summarise(NVariants = nrow(.),
                   NAdjs = unique(All),
                   Rate = round(NAdjs/NVariants, 1))
```

Factorize predictors and scale frequency

```{r,  message=TRUE, warning=TRUE}
ice <- amp %>%
  select(-SVariant)  %>%
  droplevels()
# inspect
str(ice)
```

check gradability

```{r}
summary(ice$Gradability)
```

check frequency

```{r}
summary(ice$Frequency)
```


split into varieties

```{r}
hke <- ice %>% dplyr::filter(Variety == "HKE") %>% dplyr::select(-Variety, -Speaker) %>% droplevels() %>% na.omit()
ind <- ice %>% dplyr::filter(Variety == "IndE") %>% dplyr::select(-Variety, -Speaker, -Date, -EducationLevel, -Ethnicity) %>% droplevels() %>% na.omit()
phi <- ice %>% dplyr::filter(Variety == "PhiE") %>% dplyr::select(-Variety, -Speaker, -EducationLevel, -Ethnicity) %>% droplevels() %>% na.omit()
# inspect
str(hke); str(ind); str(phi)
```


# Conditional Inference Tree Analysis{-}


## ICE-PHI{-}

```{r}
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# create initial conditional inference tree model
phi.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function + Emotionality + SemanticCategory +  Gradability, data = phi)
# extract p-values
pvals <- unlist(nodeapply(phi.ctree, ids = nodeids(phi.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
phit <- ggparty(phi.ctree) +
  geom_edge() +
  geom_edge_label(size = 3) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 10)),
                  line_gpar = list(list(size = 10), list(size = 10)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 4) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 10),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
    shared_axis_labels = TRUE)
# save
#ggsave(phit, file = here("images", "Fig4.png"), height = 6,  width = 10, dpi = 320)
# inspect
phit
```

Check accuracy of tree

```{r}
tphi <- phi %>%
  dplyr::mutate(prediction = predict(phi.ctree, newdata = phi))
confusionMatrix(data=tphi$prediction, reference = tphi$Variant)
```
check increase in accuracy by percentage points and by factor

```{r}
# percentage points
0.5643-0.3758
# improvement factor
0.5643/0.3758
```



## ICE-IND{-}




```{r}
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# create initial conditional inference tree model
ind.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function +  Emotionality + SemanticCategory +  Gradability, data = ind)
# extract p-values
pvals <- unlist(nodeapply(ind.ctree, ids = nodeids(ind.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# inspect
ind.ctree
```


```{r}
# adapt adjectives
different <- c("different")
group1 <- c("beautiful", "close", "difficult", "interesting", "nice")
group2 <- c("bad", "boring", "busy", "good", "happy", "long", "other")
group3 <- c("high", "hot")
# not in other groups
group4 <- c("big", "expensive", "funny", "great", "hard", "important", "small", "young")

ind <- ind %>%
  dplyr::mutate(Adjective = dplyr::case_when(Adjective %in%  different ~ "different",
                                             Adjective %in%  group1 ~ "g1",
                                             Adjective %in%  group2 ~ "g2",
                                             Adjective %in%  group3 ~ "g3",
                                             Adjective %in%  group4 ~ "g4",
                                             T ~ Adjective)) %>%
  dplyr::mutate(Emotionality = dplyr::case_when(Emotionality ==  "neutral" ~ "non-pos.",
                                                Emotionality ==  "negative" ~ "non-pos.",
                                                Emotionality ==  "positive" ~ "pos.",
                                                T ~ Emotionality)) %>%
  dplyr::mutate(SemanticCategory = dplyr::case_when(SemanticCategory ==  "appearance" ~ "app.",
                                             SemanticCategory ==  "evaluative" ~ "eval.",
                                             SemanticCategory ==  "descriptive" ~ "other",
                                             SemanticCategory ==  "membership" ~ "other",
                                             SemanticCategory ==  "relational" ~ "other",
                                             T ~ SemanticCategory)) %>%
  dplyr::mutate_if(is.character, factor)
# inspect
names(table(ind$Adjective))
```




```{r}
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# create initial conditional inference tree model
ind.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function +  Emotionality + SemanticCategory +  Gradability, data = ind, minbucket = 20)
# extract p-values
pvals <- unlist(nodeapply(ind.ctree, ids = nodeids(ind.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
indt <- ggparty(ind.ctree, terminal_space = 0.3,
        # id specifies node; x and y values need to be between 0 and 1
        layout = data.frame(id = c(1, 3, 4, 9),
                            x = c(0.1, 0.7, 0.4, 0.9),
                            y = c(1.0, 0.9, 0.8, 0.8))) +
  geom_edge() +
  geom_edge_label(size = 3) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 10)),
                  line_gpar = list(list(size = 10), list(size = 10)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 4) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 10),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
    shared_axis_labels = TRUE)
# save
ggsave(indt, file = here("images", "Fig5.png"),
         height = 6,  width = 10, dpi = 320)
# inspect
indt
```



Check accuracy of tree

```{r}
tind <- ind %>%
  dplyr::mutate(prediction = predict(ind.ctree, newdata = ind))
confusionMatrix(data=tind$prediction, reference = tind$Variant)
```

Check accuracy of tree

```{r}
# percentage points
0.7424-0.7314
# improvement factor
0.7424/0.7314
```


## ICE-HK{-}

```{r}
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# create initial conditional inference tree model
hke.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function + Date + Emotionality + SemanticCategory +  Gradability, data = hke)
# inspect
hke.ctree
```

```{r}
g1 <- c("beautiful", "boring", "busy", "close", "difficult", "expensive", "funny", "happy", "high", "hot", "important", "long", "other", "small", "young")
g2 <- c("bad", "big", "different", "good", "great", "hard", "interesting", "nice")

hke <- hke %>%
  dplyr::mutate(Adjective = dplyr::case_when(Adjective %in%  g1 ~ "g1",
                                             Adjective %in%  g2 ~ "g2",
                                             T ~ Adjective)) %>%
    dplyr::mutate(Emotionality = dplyr::case_when(Emotionality ==  "neutral" ~ "non-neg.",
                                                Emotionality ==  "negative" ~ "neg.",
                                                Emotionality ==  "positive" ~ "non-neg.",
                                                T ~ Emotionality)) %>%
    dplyr::mutate(SemanticCategory = dplyr::case_when(SemanticCategory ==  "appearance" ~ "app.",
                                             SemanticCategory ==  "evaluative" ~ "eval.",
                                             SemanticCategory ==  "descriptive" ~ "sem1",
                                             SemanticCategory ==  "membership" ~ "sem1",
                                             SemanticCategory ==  "relational" ~ "sem1",
                                             T ~ SemanticCategory)) %>%
  dplyr::mutate_if(is.character, factor)
```



```{r}
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# create initial conditional inference tree model
hke.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function + Date + Emotionality + SemanticCategory +  Gradability, data = hke, minbucket = 20)
# plotting
# extract p-values
pvals <- unlist(nodeapply(hke.ctree, ids = nodeids(hke.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
hket <- ggparty(hke.ctree) +
  geom_edge() +
  geom_edge_label(size = 3) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 10)),
                  line_gpar = list(list(size = 10), list(size = 10)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 4) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 10),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
    shared_axis_labels = TRUE)
# save
ggsave(hket, file = here("images", "Fig6.png"),
         height = 6,  width = 10, dpi = 320)
# inspect
hket
```


Check accuracy of tree

```{r}
thke <- hke %>%
  dplyr::mutate(prediction = predict(hke.ctree, newdata = hke))
confusionMatrix(data=thke$prediction, reference = thke$Variant)
```

Check accuracy of tree

```{r}
# percentage points

# improvement factor

```

# Outro

Extract session information

```{r amphkpie_02_93, echo=T, eval = T, message=FALSE, warning=FALSE}
sessionInfo()
``` 
